Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-12-11 presentacion_hiram/presentacion-tesis.tex
n

 \author{\scriptsize
 	Universidad de Sonora\\
 	\vspace{1px}
 	Divisi\'on de Ciencias Exactas y Naturales\\
 	\vspace{1px}
 	Departamento de Investigaci\'on en F\'isica\\
 	   \vspace{5px}
   \textbf{L.F. Hiram Ernesto Dami\'an}\\
   Defensa de tesis para obtener el grado de \\
      Maestr\'ia en Ciencias (F\'isica)\\
         \vspace{5px}
   Director:\\
   \vspace{1px}
   Jos\'e Feliciano Ben\'itez Rubio\\
\vspace{5px}
11 de Diciembre de 2019}
 \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
 %\subtitle{}
 \date{}
 \logo{\includegraphics[scale=0.1]{unison-logo.png}}
 \newcommand{\nologo}{\setbeamertemplate{logo}{}}
 %\subject{}
 \newcommand{\subf}[2]{%
   {\small\begin{tabular}[t]{@{}c@{}}
     #1\\#2
   \end{tabular}}%
 }
 %\setbeamercovered{transparent}
 %\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
	\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.
	\begin{align}
	N_R=\sigma \text{L}
	\end{align}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
%\item Experimentally
%\begin{align}
%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
%\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$

\item L is called luminosity and it is measured in cm$^{2}$s$^{-1}$.\cite{6}
\end{itemize}
\end{frame}

@@

\begin{frame}
\subsection{BDT}
\frametitle{Multivariable discriminator algorithm}
\small{
	A decision tree takes a set of input features and splits input data recursively based on
	those features.
	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
	\vspace{10px}
	BDT Variables}
\tiny{
	\begin{enumerate}
		\item	$p_t$ of the sub leading leptons
		\item 	jets with largest value of $|\eta|$
		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
		\item	Number of jets with |$\eta$| > 1.0
		\item	$\Delta\eta$ (most forward jet, closest lepton)
		\item	$\Delta\eta$ (most forward jet and b-tagged jet)
		\item 	min $\Delta$R (lepton pairs)
		\item 	$\Delta\phi$ between highest $p_t$ lepton pair
	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{enumerate} }
\end{frame}

@@

{\nologo
	\begin{frame}
	\frametitle{Kinematic variables}
		\Fontvi
		\begin{center}
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
			\end{tabular}
		\end{center}
	\end{frame}
}

{\nologo
\begin{frame}
	\begin{figure}[ht]
		\centering
		\includegraphics[scale=0.48]{figures/bdt-8var}
		\caption*{\scriptsize BDT training}
	\end{figure}
\end{frame}}

@@

\begin{frame}
\subsection{Results}
\frametitle{Post -fit Results}
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the SM. In the
			box below each distribution, the ratio of the observed and  event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}\hfill \quad
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. 
	In the box below each distribution, the ratio of the observed and event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}
\end{frame}

\begin{frame}
\frametitle{Post -fit Results}
	\begin{table}[ht!]
		\centering
		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
 Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
	\subsection{Extrapolation to higher luminosity}
\frametitle{Likelihood scan}
{\small
	\begin{itemize}
\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
\item We can define the likelihood ratio
\begin{align}
\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
\end{align}
Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
\begin{align}
q(\mu,\alpha)= -2\ln{\lambda} 
\end{align}
\item High values of $q$ represent greater incompatibility between the data and the fit model.
$q$ is a random variable with a $\chi^2$ distribution.
\end{itemize}
}
\end{frame}

@@

{\nologo
	\begin{frame}
	\frametitle{Extrapolation of luminosity for SM }
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/simple.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/simple-150.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/simple-300.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/simple-3000.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

@@

{\nologo
	\begin{frame}
	\frametitle{Extrapolation of luminosity for $k_t=-1$}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/simple-kt-1.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/simple-150-kt-1.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/simple-300-kt-1.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/simple-3000-kt-1.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

{\nologo
	\begin{frame}
	\frametitle{Likelihood scan for  $k_t=-1$}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/Likelihood-kt-1.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/Likelihood.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/Likelihood.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/Likelihood.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

>>>>

 \author{\scriptsize
 	Universidad de Sonora\\
 	\vspace{1px}
 	Divisi\'on de Ciencias Exactas y Naturales\\
 	\vspace{1px}
 	Departamento de Investigaci\'on en F\'isica\\
 	   \vspace{5px}
   \textbf{L.F. Hiram Ernesto Dami\'an}\\
   Defensa de tesis para obtener el grado de \\
      Maestr\'ia en Ciencias (F\'isica)\\
         \vspace{5px}
   Director:\\
   \vspace{1px}
  Dr. Jos\'e Feliciano Ben\'itez Rubio\\
\vspace{5px}
11 de Diciembre de 2019}
 \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
 %\subtitle{}
 \date{}
 \logo{\includegraphics[scale=0.1]{unison-logo.png}}
 \newcommand{\nologo}{\setbeamertemplate{logo}{}}
 %\subject{}
 \newcommand{\subf}[2]{%
   {\small\begin{tabular}[t]{@{}c@{}}
     #1\\#2
   \end{tabular}}%
 }
 %\setbeamercovered{transparent}
 %\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
	\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.
	\begin{align}
	N_R=\sigma \text{L}
	\end{align}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
%\item Experimentally
%\begin{align}
%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
%\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{2}$

\item L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
\end{itemize}
\end{frame}

@@

\begin{frame}
\subsection{BDT}
\frametitle{Multivariable discriminator algorithm}
\small{
	A decision tree takes a set of input features and splits input data recursively based on
	those features.
	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
	\vspace{10px}
	BDT Variables}
\tiny{
	\begin{enumerate}
		\item	$p_t$ of the sub leading leptons
		\item 	Maximum  $|\eta|$ of any  (untagged)  jet (forward jet)
		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
		\item	Number of untagged jets with |$\eta$| > 1.0
		\item	$|\Delta\eta|$ between a forward light jet and closest lepton
		\item	$|\Delta\eta|$ between a forward light jet and a b-tagged jet
		\item 	Minimum $\Delta$R between any two leptons
		\item 	$\Delta\phi$ of the highest $p_t$ same-sign lepton pair
	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{enumerate} }
\end{frame}

@@

{\nologo
	\begin{frame}
	\frametitle{Kinematic variables}
		\Fontvi
		\begin{center}
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest $p_t$)} & {Distribution of events of $\Delta\phi$ between the higher $p_t$ pair of leptons } \\
			\end{tabular}
		\end{center}
	\end{frame}
}

{\nologo
\begin{frame}
	\frametitle{BDT Training Result}
	\begin{figure}[ht]
		\centering
		\includegraphics[scale=0.48]{figures/bdt-8var}
	\end{figure}
\end{frame}}

@@

\begin{frame}
\subsection{Results}
\frametitle{Post-fit Results}
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the SM. In the
			box below each distribution, the ratio of the observed and  event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}\hfill \quad
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. 
	In the box below each distribution, the ratio of the observed and event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}
\end{frame}

\begin{frame}
\frametitle{Post-fit Results}
	\begin{table}[ht!]
		\centering
		\caption*{Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
 Pre-fit uncertainty is statistical only. Post-fit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
	\subsection{Extrapolation to high luminosity}
\frametitle{Likelihood scan}
{\small
	\begin{itemize}
\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
\item We can define the likelihood ratio
\begin{align}
\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
\end{align}
Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
\begin{align}
q(\mu,\alpha)= -2\ln{\lambda} 
\end{align}
\item High values of $q$ represent greater incompatibility between the data and the fit model.
$q$ is a random variable with a $\chi^2$ distribution.
\end{itemize}
}
\end{frame}

@@

{\nologo
	\begin{frame}
	\frametitle{Extrapolation to high luminosity for SM }
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/simple.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/simple-150.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/simple-300.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/simple-3000.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

@@

{\nologo
	\begin{frame}
	\frametitle{Extrapolation to high luminosity for $k_t=-1$ scenario}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/simple-kt-1.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/simple-150-kt-1.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/simple-300-kt-1.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/simple-3000-kt-1.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

{\nologo
	\begin{frame}
	\frametitle{Likelihood scan for $k_t=-1$ scenario}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/Likelihood-kt-1.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/Likelihood.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/Likelihood.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/Likelihood.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}
